|

### 2019-03-19 rap/article.Rmd
update

In this paper, we discuss a quantitative presentation of the Report of the Chilean National Commission on Truth and Reconciliation [-@report1991], which described more than two thousand human rights abuses perpetrated by the Pinochet regime from 1973 to 1990.

The dataset includes rich information about more than 2,0000 victims of the Pinochet regime, the geographical location of the incidents, and the specific date when the violations occurred. The graphs and maps shown in this article provide some preliminary results about the temporal and spatial variation of state-sponsored violence during the recent military period in Chile.

We believe our data opens a number of potential research avenues. First, scholars can use the dataset to evaluate the long-term impacts of human rights violations on several outcomes of interest. For example, XXX and XXX highlight that state-led violence has enduring effects on social polarisation, political outcomes, and economic development. Researchers can test whether the Pinochet regime caused a similar impact on Chile's economy and society. Moreover, sociologists and criminologists may be interested in the relationship between the intensity of the human rights abuse and post-regime levels of social unrest or interpersonal violence.

Second, the dataset enables researchers to analyse the inner dynamics of authoritarian governments. This topic remains understudied in political science due to a lack of disaggregated information. By linking human right abuses to changes in Pinochet's support coalition, scholars can explore whether the violations affected levels of civilian or bureaucratic collaboration to the regime. XXXXXXXXXXXXX.

Finally, scholars can investigate the connections between international legitimacy and domestic politics in repressive regimes. This is a promising area of research as the Chilean government and American intelligence services continue to declassify documents from the Pinochet era. One relevant question is whether pressure from foreign governments and organisations had any influence over the levels of human rights abuses in Chile. We hope our dataset is useful for scholars interested in these and other questions, and that the information it contains elicits hypotheses not only about the Pinochet period, but about authoritarian governments more generally.

>>>>

In this paper, we introduce a dataset with rich information about more than 2,000 human rights abuses perpetrated by the Pinochet regime from 1973 to 1990. We manually coded all information available in the Report of the Chilean National Commission on Truth and Reconciliation [-@report1991], and added new variables on the geographical location of the incidents and, whenever possible, the specific dates when each of the violations occurred. The graphs and maps included in this article provide some preliminary results about the temporal and spatial variation of state violence during Chile's last military government.

We believe our data open a number of potential research avenues. For instance, @lupu2017legacy, @rozenas2017political and @zhukov2018stalin highlight that state repression has enduring effects on the political preferences and social attitudes of the victims. Researchers can test whether victims of the Pinochet regime show similar changes in political behaviour. Moreover, sociologists and criminologists may be interested in the relationship between human rights abuses and post-regime levels of interpersonal violence. Recent studies have shown that democracies which arise after military regimes have higher homicide rates [@frantz2018legacy; @karstedt2006democracy], and our data can show whether areas with significant levels of military repression are also more violent today.

The dataset also enables researchers to examine how political coalitions affect the use of lethal violence in authoritarian regimes. Although the topic has received increasing attention in the last years [e.g., @fjelde2010generals; @gandhi2007authoritarian; @rivera2017authoritarian], the internal dynamics of autocratic governments remains understudied due to a lack of fine-grained information. By linking human right abuses to changes in Pinochet's support coalition, scholars can explore whether the civilian or bureaucratic collaboration to the regime impacted the number and type of violations. Since our data are presented at the individual level, they can be easily combined with legislative or bureaucratic records aggregated at any level.

Qualitative scholars may find the rich personal details about the victims particularly useful.

Lastly, scholars can investigate the connections between international legitimacy and domestic politics in repressive regimes. This is a promising area of research as the Chilean government and American intelligence services continue to declassify documents from the Pinochet era. One relevant question is whether pressure from foreign governments and organisations had any influence over the levels of human rights abuses in Chile. We hope our dataset is useful for scholars interested in these and other questions, and that the information it contains elicits hypotheses not only about the Pinochet period, but about authoritarian governments more generally.
